Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-11-09 awipev-CO2_PAR_sal.Rmd
sal / par relationship with lm()

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- tibble(
  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
) %>% 
  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
                measure_date = dmy(measure_date, tz="UTC"),
                date = as.Date(datetime)) %>% 
  dplyr::rename(ph_s_sf = pH_s_seafet,
                ph_s_dur = pH_s_durafet,
                qflag_ph_s_sf = qflag_pH_s_seafet,
                qflag_ph_s_dur = qflag_pH_s_durafet)

# Add the flag location: some samples have been collected at the pier. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
                                         datetime == as.POSIXct("2016-02-10 14:00:00") | 
                                         datetime == as.POSIXct("2016-02-17 09:20:00") |
                                         datetime == as.POSIXct("2016-02-24 14:20:00") |
                                         datetime == as.POSIXct("2016-02-04 09:30:00") |
                                         datetime == as.POSIXct("2016-01-27 15:00:00") |
                                         datetime == as.POSIXct("2016-01-13 13:45:00") |
                                         datetime == as.POSIXct("2016-01-06 14:10:00") |
                                         datetime == as.POSIXct("2015-12-24 10:45:00") |
                                         datetime == as.POSIXct("2015-12-30 13:30:00") |
                                         datetime == as.POSIXct("2018-01-05 15:20:00") |
                                         datetime == as.POSIXct("2018-02-02 14:35:00") |
                                         datetime == as.POSIXct("2018-03-02 14:10:00") |
                                         datetime == as.POSIXct("2019-05-31 11:45:00"), 
                                       1, 0))
d <- d %>%
  dplyr::filter(location_flag == 0)

# Keep only flag = 2 for at/ct analysis 
# Keep only flag = 2 for pH durafet and seaFET.
d <- d%>%
  dplyr::mutate(ct = replace(ct, qflag_ct != 2, NA),
                at = replace(at, qflag_at != 2, NA),
                ph_s_sf = replace(ph_s_sf, qflag_ph_s_sf != 2, NA),
                ph_s_dur = replace(ph_s_dur, qflag_ph_s_dur != 2, NA))

# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
d$at <- d$at * 1.0002
d$ct <- d$ct * 1.0002

# mean at and ct
at_ct_mean <- d %>% 
#  group_by(datetime)%>%
  group_by(date) %>%
  dplyr::summarize(at_mean = mean(at, na.rm = TRUE),
                   ct_mean = mean(ct, na.rm = TRUE),
                   at_sd = sd(at, na.rm = TRUE), 
                   ct_sd = sd(ct, na.rm = TRUE)
                   )
d <- left_join(d, at_ct_mean, by='date') %>% 
  dplyr::select(datetime, date, temp_s_lab, ph_s_sf, ph_s_dur, location_flag, at, ct, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
  dplyr::distinct()

# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule=2)
names(CTinterp) <- c("datetime", "ct_mean_interp")
CTinterp <- as.data.frame(CTinterp)
d$ct_mean_interp <- CTinterp$ct_mean_interp

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all %>%
                 dplyr::select(
                   c(
                     closest_datetime,
                     sal_fb,
                     temp_fb,
                     temp_mix,
                     sal_mix,
                     temp_insitu_11m,
                     temp_insitu_ctd,
                     pressure_insitu_ctd
                   )
                 ), by = "closest_datetime")

# Conversion of spec pH of in situ samples to in situ temp
pH_seafet <- d %>%
  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
pH_seafet <- pH_seafet %>% 
  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

# Conversion of spec pH of FerryBox samples to FerryBox temp
pH_durafet <- d %>%
  dplyr::filter(!is.na(ph_s_dur) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>% 
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, Pt = 0, Sit = 0))

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(date, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(date, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  dplyr::group_by(date) %>%
  dplyr::summarize(
    datetime = mean(datetime, na.rm = TRUE),
      sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE),
    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
    temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
  )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='date')
discrete <- left_join(discrete, pH_durafet_mean, by='date')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
##   *****Attention, but no longer used in the script, so no problem

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_fb <- carb$pCO2

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```

```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# ct
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ct) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pH calculated ferrybox
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, phcalc_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) # eliminate ph spec data when the profiler was at several depth during the same hour
  #dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) |
  #                                           !is.na(temp_insitu_ctd_9m), 
   #                                        ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m

# durafet pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# calculated pCO2 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, pco2_calc_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)

## bind the voltages and deployment ##

# Duplicate datetime in closest_datetime to do the left_join
d_all$closest_datetime <- d_all$datetime
discrete <- left_join(discrete, d_all %>% dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
```

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
h3{ /* Header 3 */
  font-size: 22px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h4{ /* Header 4 */
  font-size: 18px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h5{ /* Header 5 */
  font-size: 16px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
</style>

# {.tabset .tabset-fade .tabset-pills}

## Infos

### **Introduction**
<div style="text-align: justify">  
The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory. It comprises two components: (1) continuous real-time measurements and (2) discrete measurements. The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.

### **AWIPEV Underwater Observatory**
<div style="text-align: justify">  
The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems. The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured. Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP for continuous measurements of currents and waves. Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations. The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter. During this time, the system is remotely controlled and maintained from Germany. All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed. The processed data are open access and available at http://codm.hzg.de/codm.

<div style="text-align:center" markdown="1">
  <img  src="./Images/Container.png" width="200" height="200">
  <img  src="./Images/Intake.png" width="200" height="200">
  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
</div>

### **Continuous and semi-continuous measurements**
<div style="text-align: justify">  
The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015. Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry. Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit. The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading. The sensor is the first instrument in the measuring loop; data are logged every minute. This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.

Since February 2016, total alkalinity (AT) is measured every 90 min with a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through system). Fifty ml of seawater is filtered (0.2 um) using a Contros-Kongsberg cross-flow filter and then acidified using dilute hydrochloric acid (0.1 N). CO~2~ is then flushed out (open-cell titration) and the final pH measured by means of an indicator dye (bromocresol green) and visible absorption spectrometry. Together with salinity and temperature at the time of measurement, the pH reading is used to calculate AT. According to the manufacturer, the measuring range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25 umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).

In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been added to the UWO. This new sensor continuously measures pH at 11 m using an ISFET (Ion Sensitive Field Effect Transistor). According to the manufacturer, the measuring range is between 6.5 and 9 pH units, initial accuracy is 0.02 pH units and precision is 0.004 pH units. Operating salinity and temperature range are 20 to 40 PSU and 0 to 50°C respectively.

In August 2017, a Durafet III pH electrode connected to a UDA2128 Analyser (Honeywell) was also implemented to the Ferrybox flow-through system. This electrode continuously measures pH, in the Ferrybox, through an ISFET. According to the manufacturer, the measuring range is between 0 and 14 pH units.

### **Data availability**
The data at one minute frequency were tagged with the following quality flags

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 6: failing the manufacturer range test (not used)
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

* Despike using oce::despike with n=2, k=5761

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
d_min <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
                          temp_fb_qf, temp_insitu_11m_qf, ph_dur_qf, phINT_qf))

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
kable(z, digits = 1)
rm(d_min)
```

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically. Salinity from FB is taken in consideration. If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m). New column "sal_mix" is created and is the one used in ESSD paper.

+ 1 SBE45 inside the Ferrybox (sal_fb)
+ 5 CTD > 8 m depth (sal_insitu_ctd)

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_mix < 34 ~ NA_real_,
      TRUE ~ sal_mix
    )
  )
```

### **Depth profile**

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()

p_sal_range <- ggplot(data = df) +
  geom_histogram((aes(x = df$range))) +
  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
  Mytheme(size_labs = 8)
p_sal_range

kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`). The difference with depth is therefore significant.

### **Sal FB / Sal CTD 9 m **

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

print(p) #p_sal_fb_ctd

d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
```

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.

>>>>

```{r PAR / SAL relationship, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
 d_all<- d_all %>%
  dplyr::mutate(
    datetime =ymd_hms(datetime))

sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)

 sal_xts<- sal_xts %>% 
  dplyr::mutate(sal_insitu_ctd_1m = case_when(
    is.na(sal_insitu_ctd_1m) ~ 0,
    TRUE~ sal_insitu_ctd_1m))

sal_xts <- as.xts(sal_xts, order.by = as.Date(d_all$datetime))
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

#1m
fit <- lm(data = d_all, par_insitu_profile_1m ~ sal_insitu_ctd_1m)
p1 <- ggplot(d_all,aes(x=sal_insitu_ctd_1m, y= par_insitu_profile_1m, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity CTD 1 m", y="PAR Profile 1 m", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

#3m
fit <- lm(data = d_all, par_insitu_profile_3m ~ sal_insitu_ctd_3m)
p3 <- ggplot(d_all,aes(x=sal_insitu_ctd_3m, y= par_insitu_profile_3m, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity CTD 3 m", y="PAR Profile 3 m", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
#5m
fit <- lm(data = d_all, par_insitu_profile_5m ~ sal_insitu_ctd_5m)
p5 <- ggplot(d_all,aes(x=sal_insitu_ctd_5m, y= par_insitu_profile_5m, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity CTD 5 m", y="PAR Profile 5 m", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
#7m
fit <- lm(data = d_all, par_insitu_profile_7m ~ sal_insitu_ctd_7m)
p7 <- ggplot(d_all,aes(x=sal_insitu_ctd_7m, y= par_insitu_profile_7m, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity CTD 7 m", y="PAR Profile 7 m", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
#9m
fit <- lm(data = d_all, par_insitu_profile_9m ~ sal_insitu_ctd_9m)
p9 <- ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= par_insitu_profile_9m, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity CTD 9 m", y="PAR Profile 9 m", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

print(p1)
print(p3)
print(p5)
print(p7)
print(p9) 
```
